Developing a preprint culture in biology

### 2012-10-17 ms.tex

Public preprint servers allow authors to make manuscripts publicly available
before, or in parallel to, submitting them to journals for traditional
peer-review. The rationale for preprint servers is fundamentally simple: to make
the results of scientific research available to the scientific community as soon
as possible, instead of waiting until the peer-review process is fully
completed.  Sharing manuscripts using preprint servers has numerous advantages
including: 1) rapid dissemination of work-in-progress to a wider audience; 2)
improved peer review by encouraging feedback from the entire research community;
and 3) a fair and straightforward way to establish precedence.

@@

@@

Finally, public preprint servers offer a fair way to establish intellectual
priority by making the work available as soon as it is complete. Some
manuscripts will spend much more time in the review process and/or in
production after acceptance, than others. This means that publication and
acceptance dates do not accurately characterize who came up with an idea
first. For this reason, mathematicians and physicists have embraced arXiv in
part to establish priority in a fair way \cite{gin11,cal12}. This can be
especially crucial to early-career scientists. The sometimes long delay before
publication is seldom compatible with the pressure to show an impressive
publication record when applying for a scholarship or a position. Increasing
the perceived value of pre-prints as close, or equal, to journal articles (a
point we discuss in the conclusion) will allow young researchers to put their
research outcome in the open, and build a reputation for themselves through
the diffusion of their work, without the fear that this work will not be
recognized by grant or job commitees.

>>>>

Public preprint servers allow authors to make manuscripts publicly available
before, or in parallel to, submitting them to journals for traditional
peer-review. The rationale for preprint servers is fundamentally simple: to make
the results of scientific research available to the scientific community as soon
as possible, instead of waiting until the peer-review process is fully
completed.  Sharing manuscripts using preprint servers has numerous advantages
including: 1) rapid dissemination of work-in-progress to a wider audience; 2)
... %% Tim???
3) improved peer review by encouraging feedback from the entire research community;
and 4) a fair and straightforward way to establish precedence.

@@

Public preprints can be especially crucial to early-career scientists. The
sometimes long delay before publication is seldom compatible with the pressure
to show an impressive publication record when applying for a scholarship or a
position. Increasing the perceived value of pre-prints as close, or equal, to
journal articles (a point we discuss in the conclusion) will allow young
researchers to put their research outcome in the open, and build a reputation
for themselves through the diffusion of their work, without the fear that this
work will not be recognized by grant or job commitees.

@@

Finally, public preprint servers offer a fair way to establish intellectual
priority by making the work available as soon as it is complete. Some
manuscripts will spend much more time in the review process and/or in
production after acceptance, than others. This means that publication and
acceptance dates do not accurately characterize who came up with an idea
first. For this reason, mathematicians and physicists have embraced arXiv in
part to establish priority in a fair way \cite{gin11,cal12}.
